Step 13: Marginal Effects Analysis with Multiple Imputation

### 2025-09-08 reanalysis-13-marginal_effects.qmd
ame

  if (is.null(sg$subset_condition)) {
    # Overall marginal effect
    mfx <- margins(model, design = design, variables = "ever_lapse")
    test_results[[sg_name]] <- summary(mfx)
    cat(paste0("  N = ", nrow(test_data), "\n"))
  } else {
    # Subset the data and design
    subset_data <- subset(test_data, eval(sg$subset_condition))
    subset_design <- subset(design, eval(sg$subset_condition))

    if (nrow(subset_data) > 0) {
      mfx <- margins(model, 
                    design = subset_design, 
                    data = subset_data,
                    variables = "ever_lapse")
      test_results[[sg_name]] <- summary(mfx)
      cat(paste0("  N = ", nrow(subset_data), "\n"))
    } else {
      cat("  WARNING: No observations in this subgroup\n")
      test_results[[sg_name]] <- NULL
    }
  }

  # Display results if available
  if (!is.null(test_results[[sg_name]])) {
    mfx_summary <- test_results[[sg_name]]
    if ("ever_lapse" %in% rownames(mfx_summary)) {
      ame <- mfx_summary["ever_lapse", "AME"]
      se <- mfx_summary["ever_lapse", "SE"]
      cat(sprintf("  AME = %.4f (SE = %.4f)\n", ame, se))
    }
  }
}

@@

      if (is.null(sg$subset_condition)) {
        # Overall marginal effect
        mfx <- margins(model, design = design, variables = "ever_lapse")
        mfx_summary <- summary(mfx)
      } else {
        # Subset marginal effect
        subset_data <- subset(imp_data, eval(sg$subset_condition))

        if (nrow(subset_data) > 0) {
          subset_design <- subset(design, eval(sg$subset_condition))
          mfx <- margins(model, 
                        design = subset_design, 
                        data = subset_data,
                        variables = "ever_lapse")
          mfx_summary <- summary(mfx)
        } else {
          mfx_summary <- NULL
        }
      }

      # Store results
      if (!is.null(mfx_summary) && "ever_lapse" %in% rownames(mfx_summary)) {
        all_mfx_results[[sg_name]][[i]] <- list(
          ame = mfx_summary["ever_lapse", "AME"],
          se = mfx_summary["ever_lapse", "SE"],
          n = ifelse(is.null(sg$subset_condition), 
                    nrow(imp_data),
                    nrow(subset(imp_data, eval(sg$subset_condition)))),
          success = TRUE
        )
      } else {
        all_mfx_results[[sg_name]][[i]] <- list(success = FALSE)
      }
    }

>>>>

  if (is.null(sg$subset_condition)) {
    # Overall marginal effect
    mfx <- margins(model, design = design, variables = "ever_lapse_binary")
    test_results[[sg_name]] <- summary(mfx)
    cat(paste0("  N = ", nrow(test_data), "\n"))
  } else {
    # Subset the data and design
    subset_data <- subset(test_data, eval(sg$subset_condition))
    subset_design <- subset(design, eval(sg$subset_condition))

    if (nrow(subset_data) > 0) {
      mfx <- margins(model, 
                    design = subset_design, 
                    data = subset_data,
                    variables = "ever_lapse_binary")
      test_results[[sg_name]] <- summary(mfx)
      cat(paste0("  N = ", nrow(subset_data), "\n"))
    } else {
      cat("  WARNING: No observations in this subgroup\n")
      test_results[[sg_name]] <- NULL
    }
  }

  # Display results if available
  if (!is.null(test_results[[sg_name]])) {
    mfx_summary <- test_results[[sg_name]]
    if ("ever_lapse_binary" %in% rownames(mfx_summary)) {
      ame <- mfx_summary["ever_lapse_binary", "AME"]
      se <- mfx_summary["ever_lapse_binary", "SE"]
      cat(sprintf("  AME = %.4f (SE = %.4f)\n", ame, se))
    }
  }
}

@@

      if (is.null(sg$subset_condition)) {
        # Overall marginal effect
        mfx <- margins(model, design = design, variables = "ever_lapse_binary")
        mfx_summary <- summary(mfx)
      } else {
        # Subset marginal effect
        subset_data <- subset(imp_data, eval(sg$subset_condition))

        if (nrow(subset_data) > 0) {
          subset_design <- subset(design, eval(sg$subset_condition))
          mfx <- margins(model, 
                        design = subset_design, 
                        data = subset_data,
                        variables = "ever_lapse_binary")
          mfx_summary <- summary(mfx)
        } else {
          mfx_summary <- NULL
        }
      }

      # Store results
      if (!is.null(mfx_summary) && "ever_lapse_binary" %in% rownames(mfx_summary)) {
        all_mfx_results[[sg_name]][[i]] <- list(
          ame = mfx_summary["ever_lapse_binary", "AME"],
          se = mfx_summary["ever_lapse_binary", "SE"],
          n = ifelse(is.null(sg$subset_condition), 
                    nrow(imp_data),
                    nrow(subset(imp_data, eval(sg$subset_condition)))),
          success = TRUE
        )
      } else {
        all_mfx_results[[sg_name]][[i]] <- list(success = FALSE)
      }
    }
